Balancing local frequency content in seismic data using non-stationary smoothing

### 2018-04-23 chapter-conclusion/paper.tex
done... can't get thesis to compile though!

This chapter also discusses two applications of these algorithms---the frequency balancing algorithm was demonstrated on an application on matching high-resolution and legacy seismic images, and the modified algorithm was demonstrated on an application of multicomponent seismic image registration.

@@

Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
It is realized that the least-squares Hessian can calculated by solving a data matching problem between two conventionally migrated images, and can be represented by the combination of amplitude and frequency balancing operations.
An example is applied to a 2D synthetic Sigsbee data set.

\subsection{Future work}
In the future, the work presented in chapter 5 should be extended to involve real data and 3D examples. 
It also could benefit by comparing the results of the proposed approach taken in the chapter to other previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debflt,prestack,poststack}, to see how it compares in different situations.

Another component to data matching may incorporate the phase of the signal to be matched. 
Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems may benefit from these corrections.

@@

\subsection{Code}
The examples in this thesis were implemented with the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagacsar}.
The package is available at \url{http://www.ahay.org/}.

>>>>

This chapter also discusses two applications of these algorithms---the frequency balancing algorithm was demonstrated on an application of matching high-resolution and legacy seismic images, and the modified algorithm was demonstrated on an application of multicomponent seismic image registration.

@@

Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
An approximation to the least-squares Hessian can calculated by solving a data matching problem between two conventionally migrated images, and can be represented by the combination of amplitude and frequency balancing operations.
An example is applied to a 2D synthetic Sigsbee data set.

\subsection{Future work}
In the future, the work presented in chapter 5 should be extended to involve real data and 3D examples. 
It also could benefit by comparing the results of the proposed approach taken in the chapter to other previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debfilt,prestack,poststack}, to see how it compares in different situations.

Another extension of this data matching procedure may be to incorporate
%Another component to data matching may incorporate 
the phase of the signal to be matched. 
Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems may benefit from these corrections.

@@

\subsection{Code}
The examples in this thesis were implemented with the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagascar}.

The package is available at \url{http://www.ahay.org/}.

### 2018-04-23 chapter-intro/paper.tex
done... can't get thesis to compile though!

The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable}.
These two images will always be plotted in grayscale.
In parts of this thesis, I will show a 2D line from this 3D data set for simplicity of plotting.

>>>>

The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable,data}.
These two images will always be plotted in grayscale.
In parts of this thesis, I will show a 2D line from this 3D data set for simplicity of plotting.

### 2018-04-23 chapter-locfreq/paper.tex
done... can't get thesis to compile though!

%\section{Examples}
        This method is applicable to workflows that require matching data with different frequency content. 
        Here, we demonstrate that using this algorithm to match high-resolution and legacy seismic images produces better results.

%        \subsection{Matching legacy and high-resolution images}
        High-resolution seismic data, such as those acquired with the P-cable acquisition system, can produce very detailed images of the near subsurface \cite[]{tip}. 
        When compared to conventional seismic images, high-resolution images have a higher dominant frequency and a larger frequency bandwidth. 
        However, they usually lack low frequency content and depth coverage that is present in conventional seismic images. 
        As a result, successful interpretation of high-resolution images can be aided by matching with legacy data coverage over the same area.

@@

%\subsection{Multicomponent image registration}
\subsection{Iterative method for calculating the smoothing radius: A modification}
        The algorithm previously presented works well in cases when one data set has clearly higher frequency content than the other.
        %However, this need not always be the case.
        However, in some cases, the two data sets may have similar local frequency content, but they may still need to be matched.
        We illustrate a modified version of the previous algorithm by demonstrating it on an example of multi-component seismic image registration.

@@

        We modify the objective in equation (\ref{eq:obj}) as
            \begin{equation}
                \label{eq:obj2}
                \min_{\mathbf{R} \in [-N, -1] \cup [1, N]} \Big \Vert \mathbf{F}[
                \mathbf{S}_{\mathbf{R}_p} \mathbf{d}_{p} ] - \mathbf{F}[
                \mathbf{S}_{\mathbf{R}_s}\mathbf{d}_{s}] \Big \Vert\;, 
            \end{equation}
        %were $S_{R_p}$ and $S_{R_s}$ are the non-stationary smoothing operators for the PP and
        %SS images, respectively, and 
        where $\mathbf{d}_p$ and $\mathbf{d}_s$ are the PP and SS images, respectively, and
        $\mathbf{S}_{\mathbf{R}_p}$ and $\mathbf{S}_{\mathbf{R}_s}$ are the non-stationary smoothing
        operators for the PP and SS images, respectively.
        We also modify the residual from equation (\ref{eq:residual}) as
            \begin{equation}
                \label{eq:residual2}
                \mathbf{r} = \mathbf{F}[\mathbf{S}_{\mathbf{R}_{p}}\mathbf{d}_p] -
                \textbf{F}[\mathbf{S}_{\mathbf{R}_s}\mathbf{d}_s]\;.
            \end{equation}
        The ideal radius is still found using the same line-search from equation (\ref{eq:alg}),
        except we allow the smoothing radius to be negative. Physically, a negative smoothing radius
        would signify that the image should be sharpened at that particular point instead of
        smoothed. In this case, instead of trying to sharpen the PP image at that particular point, 
        we
        %choose to smooth the SS image by the negative component of the smoothing radius. Thus, we
        %define $\mathbf{R}_p$ anda $\mathbf{R}_s$ at each sample as
        %\begin{equation}
        %        \mathbf{R}_p = \begin{cases} \mathbf{R} &\mbox{if } \mathbf{R} \ge 1 \\
        %1 & \mbox{otherwise} \end{cases} 
        %\end{equation}
        %and
        %\begin{equation}
        %        \mathbf{R}_s = \begin{cases} |\mathbf{R}| &\mbox{if } \mathbf{R} \le -1 \\
        %1 & \mbox{otherwise} \end{cases} 
        %\end{equation}
        %choose to smooth the SS image by the negative component of the smoothing radius. Thus, we
        %define the $i$th components of $\mathbf{R}_p$ and $\mathbf{R}_s$ as
        choose to smooth the SS image by the negative part of the smoothing radius. 
        Thus, we define the $i$th components of $\mathbf{R}_p$ and $\mathbf{R}_s$ as
        %Thus, we define $R_{p,i}$ and $R_{s,i}$ (the $i$th components of $\mathbf{R}_p$ and
        %$\mathbf{R}_s$) as
        \begin{equation}
                R_{p,i} = \begin{cases} R_{i} &\mbox{if } R_{i} \ge 1 \\
        1 & \mbox{otherwise} \end{cases} 
        \end{equation}
        and
        \begin{equation}
                R_{s,i} = \begin{cases} |R_{i}| &\mbox{if } R_{i} \le -1 \\
        1 & \mbox{otherwise} \end{cases} 
        \end{equation}

        where $R_i$ is the $i$th component of $\mathbf{R}$ and a radius of 1 represents no
        smoothing. This allows each image to be smoothed in different areas to balance the frequency
        content between the two images.

@@

\section{Acknowledgements}
        We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their
        financial support.
%
%\onecolumn
%
%\bibliographystyle{seg}
%\bibliography{SEG,locfreq}

>>>>

        This method is applicable to workflows that require matching data with different frequency content. 
        Here, we demonstrate that using this algorithm to match high-resolution and legacy seismic images produces better results.

        High-resolution seismic data, such as those acquired with the P-cable acquisition system, can produce very detailed images of the near subsurface \cite[]{tip}. 
        When compared to conventional seismic images, high-resolution images have a higher dominant frequency and a larger frequency bandwidth. 
        However, they usually lack low frequency content and depth coverage that is present in conventional seismic images. 
        As a result, successful interpretation of high-resolution images can be aided by matching with legacy data coverage over the same area.

@@

\subsection{Iterative method for calculating the smoothing radius: A modification}
        The algorithm previously presented works well in cases when one data set has clearly higher frequency content than the other.
        %However, this need not always be the case.
        However, in some cases, the two data sets may have similar local frequency content, but they may still need to be matched.
        We illustrate a modified version of the previous algorithm by demonstrating it on an example of multi-component seismic image registration.

@@

        We modify the objective in equation (\ref{eq:obj}) as
            \begin{equation}
                \label{eq:obj2}
                \min_{\mathbf{R} \in [-N, -1] \cup [1, N]} \Big \Vert \mathbf{F}[
                \mathbf{S}_{\mathbf{R}_p} \mathbf{d}_{p} ] - \mathbf{F}[
                \mathbf{S}_{\mathbf{R}_s}\mathbf{d}_{s}] \Big \Vert\;, 
            \end{equation}
        where $\mathbf{d}_p$ and $\mathbf{d}_s$ are the PP and SS images, respectively, and $\mathbf{S}_{\mathbf{R}_p}$ and $\mathbf{S}_{\mathbf{R}_s}$ are the non-stationary smoothing operators for the PP and SS images, respectively.
        We also modify the residual from equation (\ref{eq:residual}) as
            \begin{equation}
                \label{eq:residual2}
                \mathbf{r} = \mathbf{F}[\mathbf{S}_{\mathbf{R}_{p}}\mathbf{d}_p] -
                \textbf{F}[\mathbf{S}_{\mathbf{R}_s}\mathbf{d}_s]\;.
            \end{equation}
        The ideal radius is still found using the same line-search from equation (\ref{eq:alg}), except we allow the smoothing radius to be negative. 
        Physically, a negative smoothing radius would signify that the image should be sharpened at that particular point instead of smoothed. 
        In this case, instead of trying to sharpen the PP image at that particular point, we choose to smooth the SS image by the negative part of the smoothing radius. 
        Thus, we define the $i$th components of $\mathbf{R}_p$ and $\mathbf{R}_s$ as 
        \begin{equation}
                R_{p,i} = \begin{cases} R_{i} &\mbox{if } R_{i} \ge 1 \\
        1 & \mbox{otherwise} \end{cases} 
        \end{equation}
        and
        \begin{equation}
                R_{s,i} = \begin{cases} |R_{i}| &\mbox{if } R_{i} \le -1 \\
        1 & \mbox{otherwise} \end{cases} 
        \end{equation}
        where $R_i$ is the $i$th component of $\mathbf{R}$ and a radius of 1 represents no smoothing. 
        This allows each image to be smoothed in different areas to balance the frequency content between the two images.

@@

\section{Acknowledgements}
        We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.
